\section{Takeout double}

At least 10 points with perfect shape. Unbid suits should have at least 3 cards, unless 44(32) over a minor.

Prefer to double rather than overcall at a 1- or 2-level with a 5 card minor if support for other suits is ok.

If you can overcall your five-card major at 1-level, do not make a takeout double  unless you have a good enough hand to double and then bid your major.

\section{Responsive double}

We play the responsive double when LHO opens the bidding with a suit, your partner makes a 3-suit takeout double or an overcall and RHO raises. We play responsive double up to RHO 3\S. The responsive double shows at least 44 unbid suits if partner made an overcall, major suits if partner doubled and opponents are bidding a minor, or minor suits if partner doubled and opponents are bidding a major.

Typical auctions would be:

\begin{tabular}{lll}
(1\m)---\X---(2/3\m)---\X & = & 44\+\MM \\
(1\M)---\X---(2/3\M)---\X & = & 44\+\mm \\
(1$X$ )---1$Y$ ---(2/3$X$ )---\X & = & 44\+$ZW$  \\
\end{tabular}

Responsive doubles are on also over an artificial opening promising a specific suit, an artificial raise, and over raises of weak 2 bids. For example:

\begin{tabular}{l}
(1\S)---\X---(2\C\ constructive \S\ raise)---\X\\
(1\H\ showing 5\S)---\X---(2\S)---\X\\
(2\D)---\X---(D\M)---\X \\
\end{tabular}

At least 6 points at 2-level and 8 points at 3-level.

Responsive doubles are off:
\begin{itemize}
    \item If partner's overcall was not a natural, non-jump bid of a suit. For example

    \begin{tabular}{l}
    (1\H)---2\S---(3\H)\\
    (1\D)---(2\D Michaels)---(3\D)\\
    (1\H)---1\N\footnotemark---(2\H)\\
    \end{tabular}
    \footnotetext{There is some merit to playing responsive doubles after strong 1\N\ overcall, but we currently do not.}

    \item If the opponents have not confirmed a fit. For example

    \begin{tabular}{l}
    (1\S)---\P---(\P)---\X---(2\S)\\
    (1\D)---\P---(1\S)---\X---(2\D)\\
    (1\H)---\X---(1\S)\\
    \end{tabular}
\end{itemize}
