Unless otherwise specified, the following general principles apply to all constructive, competitive and defensive bidding:
\begin{itemize}
    \item The first naturally bid suit is (at least) a 5-card suit.
    \item The second suit bid is (at least) a 4-card suit.
    \item With two 5-card suits, bid the higher one first.
    \item With two 4-card suits, bid the lower one first (the one you can bid at a lower level).
    \item A new suit bid by responder is forcing for one round (F1), except when their strength is limited from above (e.g. they have previously passed).
    \item A natural \N\ bid is not forcing.
    \item A jump is always weak and pre-emptive when it can be weak (it is your first bid or you have previously only passed).
    \item A jump is strong (maximum hand if your strength is limited; F1 if it is not) when it cannot be weak (you have already shown some points) or when there have already been two consecutive passes before you (then there is no point in pre-empting, because your pass would end the auction).
    \item Repeating your own suit is not forcing. Repeating it with a jump is forcing.
    \item Repeating your own suit in a free position (partner's last bid was not forcing or an opponent intervened), in a game-forcing (FG) situation, or higher than the nearest \N\ bid shows the suit to be one card longer.
    \item Repeating your own suit after partner's forcing bid, below the nearest \N\ bid, does not promise extra length, but instead shows a weaker hand (e.g. 1\H---2\C---2\H).
    \item Fourth-suit forcing: if three suits have been bid naturally by our side, bidding the fourth suit is artificial and forcing (FG).
    \item A game bid is generally sign-off.
    \item Supporting partner's suit below game is usually invitational. It is not invitational after partner's pre-emptive bid (it is pre-emptive) and not in an FG situation (where it shows a stronger hand than jumping to game).
\end{itemize}

Unless otherwise specified, in competitive and defensive bidding:
\begin{itemize}
    \item Responder's bids at 1-level and 3-level are F1.
    \item Responder's bids at 2-level are non-forcing (except cuebids).
    \item \N\ promises a stopper in opponent's suit.
    \item 2-level cuebids are at least invitational, and if partner has bid a major also show support.
    \item 3-level cuebids ask for stopper, except direct cues 3\C\D\H\ when partner has bid a major, which shows at least invitational support.
\end{itemize}